On Determinism of Game Engines used for Simulation-based Autonomous Vehicle Verification

### 2020-11-13 paper/cav_determinisim_main.tex
GC abstract

\begin{abstract}
\noindent 
Game engines are increasingly used as simulation platforms by the autonomous vehicle (AV) community to develop vehicle control systems and test environments. 
%
A deterministic process has no randomness and will always produce the same output with the same initial conditions and event history. 
%
Determinism is a key requirement for simulation-based development and verification; it ensures tests are repeatable, so that software bugs can be found and fixed, and simulation results are trustworthy.
\todo[inline,color=green!40]{GC Alternative: Determinism is a key requirement for simulation-based development and verification; it ensures the simulation is precise and that tests are repeatable, so that software bugs can be found and fixed, and simulation results are trustworthy.}
%
% KIE: Ideally, these engines are deterministic, but we've found that they are not. :(
% These engines must be deterministic for finding and resolving defects (bugs) in software and ensuring auditable and repeatable tests can be executed for verification and validation (V\&V). 
%
However, game engines do not need to be deterministic per se. % when used for games. 
%
This paper identifies the requirements these engines need to fulfil when used for AV development and testing, and proposes a method to determine the \textit{simulation precision} for specific configurations and utilisation of the software and hardware, respectively. 
%
\todo[inline,color=red!40]{old: A case study using CARLA, an open-source simulation environment powered by Unreal Engine, illustrates the proposed method and results from an example scenario indicate the presence of a deterministic operational simulation setup.}
%
A case study using CARLA, an open-source autonomous driving simulation environment powered by Unreal Engine (game engine), illustrates the proposed method and results from an example scenario demonstrate simulation precision to an acceptable tolerance.
%
\textbf{ALTERNATIVE: This empirical investigation using CARLA, an open-source autonomous driving simulation environment powered by Unreal Engine, has highlighted the shortcomings of using a games engine for simulation based verification and advice for best working practice.}

>>>>

\begin{abstract}
\noindent 
Game engines are increasingly used as simulation platforms by the autonomous vehicle (AV) community to develop vehicle control systems and test environments. 
%
A deterministic process has no randomness and will always produce the same output with the same initial conditions and event history. 
%
Determinism is a key requirement for simulation-based development and verification; it ensures tests are repeatable, so that software bugs can be found and fixed, and simulation results are trustworthy.
\todo[inline,color=green!40]{GC Alternative: Determinism is a key requirement for simulation-based development and verification; it ensures the simulation is precise and that tests are repeatable, so that software bugs can be found and fixed, and simulation results are trustworthy.}
%
% KIE: Ideally, these engines are deterministic, but we've found that they are not. :(
% These engines must be deterministic for finding and resolving defects (bugs) in software and ensuring auditable and repeatable tests can be executed for verification and validation (V\&V). 
%
However, game engines do not need to be deterministic per se. % when used for games. 
%
This paper identifies the requirements these engines need to fulfil when used for AV development and testing, and proposes a method to determine the \textit{simulation precision} for specific configurations and utilisation of the software and hardware, respectively. 
%
\todo[inline,color=red!40]{old: A case study using CARLA, an open-source simulation environment powered by Unreal Engine, illustrates the proposed method and results from an example scenario indicate the presence of a deterministic operational simulation setup.}
%
A case study using CARLA, an open-source autonomous driving simulation environment powered by Unreal Engine has highlighted the shortcomings of using a games engine for simulation based verification. The proposed method and results from an example scenario demonstrate simulation precision to an acceptable tolerance.
%
% \textbf{ALTERNATIVE: This empirical investigation using CARLA, an open-source autonomous driving simulation environment powered by Unreal Engine, has highlighted the shortcomings of using a games engine for simulation based verification and we present advice for best working practice.}
